Cross-validation of regression models: mixed model examples (edited)

### 2023-10-11 scratch/gm_addition_to_cv-edited.Rmd
increase n of clusters to 100 in mixed models addendum to vignette

# Parameters:
set.seed(123) # set.seed(9693)
Nb <- 10     # number of groups
Nw <- 5      # number of individuals within groups
Bb <- 0      # between-group regression coefficient on group mean
SDre <- 2.0  # between-group SD of random level relative to group mean of x
SDwithin <- 0.5  # within group SD
Bw <- 1  # within group effect of x

@@

```{r plot1}
#| out.width = "100%",
#| fig.height = 6,
#| fig.cap = "Hierarchical data set with 10 clusters"
plot <- xyplot(y ~ x, data=Data, group=group,
               ylim=c(0, 20),
               par.settings=list(superpose.symbol=list(pch=1, cex=0.7))) +
    layer(panel.ellipse(..., center.cex=0))
plot
```

@@

Data_long <- reshape(Data, direction = "long", sep = ".", 
              timevar = "effect", varying = grep("\\.", names(Data)))
Data_long$id <- 1:nrow(Data_long)
Data_long <- reshape(Data_long, direction = "long", sep = "_", 
              timevar = "modelcode",  varying = grep("_", names(Data_long)))

@@

```{r cross-validation}
#| out.width = "100%",
#| fig.height = 6,
#| fig.cap = "Cross-validation comparing random intercept models with varying fixed effects and with case- and cluster-based resampling."
modlist <- models("~ 1"=fit0, "~ x"=fit1, "~ x + xm"=fit2)
cvs_cases <- cv(modlist, data=Data, seed=9693)
cvs_clusters <- cv(modlist, data=Data, cluster="group")

>>>>

# Parameters:
set.seed(9693) # set.seed(123) 
Nb <- 100     # number of groups
Nw <- 5      # number of individuals within groups
Bb <- 0      # between-group regression coefficient on group mean
SDre <- 2.0  # between-group SD of random level relative to group mean of x
SDwithin <- 0.5  # within group SD
Bw <- 1  # within group effect of x

@@

```{r plot1}
#| out.width = "100%",
#| fig.height = 6,
#| fig.cap = "Hierarchical data set with 10 clusters"
plot <- xyplot(y ~ x, data=Data[ 1:50,], group=group,
               ylim=c(0, 20),
               par.settings=list(superpose.symbol=list(pch=1, cex=0.7))) +
    layer(panel.ellipse(..., center.cex=0))
plot
```

@@

Data_long <- reshape(Data[1:50, ], direction = "long", sep = ".", 
              timevar = "effect", varying = grep("\\.", names(Data.10)))
Data_long$id <- 1:nrow(Data_long)
Data_long <- reshape(Data_long, direction = "long", sep = "_", 
              timevar = "modelcode",  varying = grep("_", names(Data_long)))

@@

```{r cross-validation}
#| out.width = "100%",
#| fig.height = 6,
#| fig.cap = "Cross-validation comparing random intercept models with varying fixed effects and with case- and cluster-based resampling."
modlist <- models("~ 1"=fit0, "~ x"=fit1, "~ x + xm"=fit2)
cvs_cases <- cv(modlist, data=Data, seed=9693)
cvs_clusters <- cv(modlist, data=Data, cluster="group", k=10, seed=6449)
